Object naming is context-dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
small modifications

Understanding and modeling the way humans converse about their environment using natural language has been a long-standing goal of research in various fields related to artificial intelligence and linguistics.
With recent  developments in computer vision and a range of massive data collections in particular, there has been a veritable explosion of interest in language \& vision tasks, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,chen2015mind,vinyals:show,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016,schlazar:acl16}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}.
In principle, the underlying data collections here should not only spur computational, application-oriented research aimed at implementing systems for very specific tasks -- they should also constitute extremely valuable resources for research aimed at deriving linguistic generalizations about various phenomena related to language grounding, reference and situated interaction which, for a long time, have been investigated mostly in very controlled and small-domain experimental settings, cf. \cite{anderson1991hcrc,fernangen:sigd07,krahmer:2012,takenobu2012rex,zarriess2016pentoref} for some examples of traditional data collections related to reference and grounding.  
In turn, these linguistic generalizations could inform computational modeling, architecture design and future data collections.
However, so far, studies that have tested linguistic hypotheses on large-scale vision \& language resources have been relatively rare.

@@

\begin{figure}[t]
	\begin{center}
		\begin{minipage}{.35\textwidth}
			\includegraphics[width=4.2cm]{fig/graffig.jpg}
		\end{minipage}
		\begin{minipage}{.2\textwidth}
			\includegraphics[height=2cm,width=2.5cm]{fig/visual_genome_dogs.png}
		\end{minipage}
	\begin{minipage}{.2\textwidth}
		\includegraphics[height=2cm,width=2.5cm]{fig/flickr_1003163366_dog_boxes_crop.jpg}
	\end{minipage}
	\begin{minipage}{.2\textwidth}
		\includegraphics[height=2cm,width=2.5cm]{fig/refcoco_2400_dog_boxes_crop.jpg}
	\end{minipage}\vspace{-0cm}\\
\begin{minipage}{.35\textwidth}
	---
\end{minipage}
\begin{minipage}{.2\textwidth}
	\tiny
	{\textsl{dalmatian, dog, heeler}}
\end{minipage}
\begin{minipage}{.2\textwidth}
	\textsl{\tiny dog}
\end{minipage}
\begin{minipage}{.2\textwidth}
	\tiny \textsl{dog}
\end{minipage}
	\end{center}
	\caption{Experimental and real-world visual scenes showing dogs (GET MORE IMAGES OF DOGS FROM VG???)}
	\label{fig:graf_genome}
\end{figure}

@@

\begin{itemize}   
		\item[(1)] the \textbf{specific category} of the object that the speaker referred to 
		\item[(2)] \textbf{exhaustive annotations} for all the other objects in the scene (i.e. distractors)
		\item[(3)] the \textbf{natural name} chosen by a speaker for describing or referring to an object

@@

@@

\begin{itemize}
     		\item[(1)] \textbf{Specific categories}: not available, the $80$~COCO categories tend to be entry-level categories and are not linked to the ImageNet taxonomy. \cs{TODO: EX / ANALYSIS}
		\item[(2)] \textbf{Exhaustive annotations}: not available, as not all objects were annotated with REs and corresponding categories
		   \item[(3)] \textbf{Natural names}: available, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
\end{itemize}

@@

As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent and dense annotations of object categories at a sufficient level of specificity. We now discuss tentative solutions to the shortcomings for this problem.

@@

\subsection{Exhaustive, automatic object labeling}

One solution for obtaining objects labels at a consistent, specific level in a certain taxonomy would be to train and/or apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers. 
However, pre-trained models only exist for a subset of the datasets' objects. \cs{TODO: ADD CMP WITH ILSVRC}
For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans. 
Thus, it is unclear whether it is actually feasible to exhaustively label e.g. all objects in VisualGenome images with their corresponding leaf node in ImageNet, at a decent level of quality.

>>>>

Understanding and modeling the way humans converse about their environment using natural language has been a long-standing goal of research in various fields related to artificial intelligence and linguistics.
With recent  developments in computer vision and a range of massive data collections in particular, there has been a veritable explosion of interest in language \& vision tasks, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}.
In principle, the underlying data collections here should not only spur computational, application-oriented research aimed at implementing systems for very specific tasks -- they should also constitute extremely valuable resources for research aimed at deriving linguistic generalizations about various phenomena related to language grounding, reference and situated interaction which, for a long time, have been investigated mostly in very controlled and small-domain experimental settings, cf. \cite{anderson1991hcrc,fernangen:sigd07,krahmer:2012,takenobu2012rex,zarriess2016pentoref} for some examples of traditional data collections related to reference and grounding.  
In turn, these linguistic generalizations could inform computational modeling, architecture design and future data collections.
However, so far, studies that have tested linguistic hypotheses on large-scale vision \& language resources have been relatively rare.

@@

\begin{figure}[t]
	\begin{center}
		\begin{minipage}{.35\textwidth}
			\includegraphics[width=4.2cm]{fig/graffig.jpg}
		\end{minipage}
		\begin{minipage}{.2\textwidth}
			\includegraphics[height=2cm,width=2.5cm]{fig/visual_genome_dogs.png}
		\end{minipage}
	\begin{minipage}{.2\textwidth}
		\includegraphics[height=2cm,width=2.5cm]{fig/flickr_1003163366_dog_boxes_crop.jpg}
	\end{minipage}
	\begin{minipage}{.2\textwidth}
		\includegraphics[height=2cm,width=2.5cm]{fig/refcoco_2400_dog_boxes_crop.jpg}
	\end{minipage}\vspace{-0cm}\\
\begin{minipage}{.35\textwidth}
	---
\end{minipage}
\begin{minipage}{.2\textwidth}
	\tiny
	{\textsl{dalmatian, dog, heeler}}
\end{minipage}
\begin{minipage}{.2\textwidth}
	\textsl{\tiny dog}
\end{minipage}
\begin{minipage}{.2\textwidth}
	\tiny \textsl{dog}
\end{minipage}
	\end{center}
		\vspace{-0.8cm}

	\caption{Experimental and real-world visual scenes showing dogs from Visual Genome, RefCoco, and Flickr)}
	\label{fig:graf_genome}
		\vspace{-0.5cm}

\end{figure}

@@

\begin{itemize}   
		\item[(1)] the \textbf{specific category} of the object that the speaker referred to 
		\item[(2)] \textbf{exhaustive annotations} for all the other objects in the scene (i.e. distractors)
		\item[(3)] the \textbf{natural name} chosen by a speaker for referring to an object

@@

In the following, we will discuss datasets that provide descriptions or referring expressions for objects in real-world images and could, in principle,  be suitable for studying object naming. We focus on collections  that have been used for object recognition, referring expression generation, phrase localization in previous work, but do not discuss other collections for e.g. image captioning which typically do not link mentions of objects to corresponding image regions.

@@

\begin{itemize}
     		\item[(1)] \textbf{Specific categories}: not available, the $80$~COCO categories tend to be entry-level categories and are not linked to the ImageNet taxonomy (e.g.,~\cat{bird, person, car, bus})
		\item[(2)] \textbf{Exhaustive annotations}: not available, as not all objects were annotated with REs and corresponding categories
		   \item[(3)] \textbf{Natural names}: available, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
\end{itemize}

@@

As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent and dense annotations of object categories at a sufficient level of specificity. We now discuss tentative solutions.

@@
